Races with hyper3 objects

### 2022-05-22 inst/race3.Rmd
clarification and test H0: p=0.5

above, we see close agreement with the theoretical value of
$(\sqrt{2}-1,1-\sqrt{2})\simeq (0.414,0.586)$

At the evaluate of $\hat{a}=\sqrt{2}-1$ we can show that
$\log\mathcal{l}(\hat{a})=\log\left(3-2\sqrt{2}\right)\simeq -1.76$.
Defining $\mathcal{S}=\log\mathcal{L}$ as the support [log-likelihood]
we have

@@

as a standard support function which has a maximum value of zero.
Further, we can use either analytical or numerical methods to find a
credible interval.  With an $n$-unit of support criterion the
analytical solution to $\mathcal{S}(p)=-2$ is given by defining
$X=\log(3-2\sqrt{2})-n$ and solving $p(1-p)/(1+p)=X, or
$\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the lower
and upper limits of the credible interval.  Graphically:

>>>>

above, we see close agreement with the theoretical value of
$(\sqrt{2}-1,1-\sqrt{2})\simeq (0.414,0.586)$.  Observe that the
maximum likelihood estimate for $a$ is strictly less than 0.5, even
though the finishing order is symmetric.  Using
$\mathcal{L}(a)=\frac{a(1-a)}{1+a}$, we can show that
$\log\mathcal{L}(\hat{a})=\log\left(3-2\sqrt{2}\right)\simeq -1.76$,
where $\hat{a}=\sqrt{2}-1$ is the maximum likelihood estimate for $a$.
Defining $\mathcal{S}=\log\mathcal{L}$ as the support [log-likelihood]
we have

@@

as a standard support function which has a maximum value of zero when
evaluated at $\hat{a]=\sqrt{2}-1$.  For example, we can test the null
that $a=b=\frac{1}{2}$, the statement that the competitors have equal
Bradley-Terry strengths:

```{r}
a <- 1/2 # null
(S_delta <- log( a*(1-a)/(1+a))- log(3-2*sqrt(2)))
```

Thus the additional support gained in moving from $a=\frac{1}{2}$ to
the evaluate of $a=\sqrt{2}-1$ is 0.029, rather small [as might be
expected given that we have only one rather uninformative observation,
and also given that the maximum likelihood estimate ($\simeq 0.41$) is
quite close to the null ($0.5$).  Nevertheless we can apply Wilks's
theorem for a $p$-value:

```{r}
pchisq(-2*S_delta,df=1,lower.tail=FALSE)
```

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}.

Further, we can use either analytical or numerical methods to find a
credible interval.  With an $n$-unit of support criterion the
analytical solution to $\mathcal{S}(p)=-2$ is given by defining
$X=\log(3-2\sqrt{2})-n$ and solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval.  Graphically:
